*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-05 Code/Manuscript_O2.Rmd
minor edit

The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B,C). In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR. 
In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), and no evidence of inhibition of growth at any achieved cumulative diel PUR.  Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*. [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light. For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)A,B and C.

@@

Under both 25 and 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes. The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.  Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E). For distinct fits for different photoperiods refer to figure \@ref(fig:PhotoperiodPurFitsPlots)D,E and F.

@@

As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)G,H).  Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for different photoperiod fits refer to figure \@ref(fig:PhotoperiodPurFitsPlots)G,H and I.

>>>>

The representative of HLI clade, *P. marinus* MED4, showed no growth under any 4 h photoperiod treatments, even when a 4 h photoperiod delivered cumulative diel PUR equivalent to other photoperiod treatments (Figure \@ref(fig:PhotoperiodPurFitsPlots)A,B,C). In parallel MED4 showed no growth under 2.5 µM O~2~, no matter the level of diel cumulative PUR. 
In contrast, under 250 or 25  µM O~2~, and under any photoperiod greater than 4 h, MED4 growth under blue light was well described by a saturating response of growth [@harrisonPhotosynthesisirradianceRelationshipsPolar1986] to increasing cumulative diel PUR, with saturation of growth rate achieved around  1.0 x 10^6^ µmol m^-2^d^-1^ (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), and no evidence of inhibition of growth at any achieved cumulative diel PUR.  Under the 'artificial' growth treatment of red light, MED4 achieved more growth per unit diel cumulative PUR (Figure \@ref(fig:BluevsRedPurFitsPlots)A,B), consistent with Murphy *et al*. [@murphyPhotoinactivationPhotosystemII2017], who showed a lower cost for growth under red light, for MED4, because red light provokes less photoinactivation of PSII, than equivalent levels of blue light. For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) A,B and C.

@@

Under both 25 and 250 µM O~2~ experiments, SS120 growth plateaued by about 5.0 x 10^5^ µmol photons m^-2^ d^-1^ diel PUR, with some scatter among photoperiod and spectral waveband regimes. The onset of growth inhibition extended to higher cumulative diel PUR for cultures under 25 µM O~2~, showing that SS120 is partially protected from photoinhibition of growth by 25 µM O~2~.  Under 25 µM O~2~, red light again generated more growth of SS120 per unit cumulative diel PUR, than did blue light, again consistent with lower cost of growth through lower photoinactivation under red light (Figure \@ref(fig:BluevsRedPurFitsPlots)E). For distinct fits for different photoperiods refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) D,E and F.

@@

As with MED4 and SS120, our data again support enhanced growth under conditions of low cumulative diel PUR and 660 nm (red) spectral bandwidth, consistent with Murphy *et al*.[@murphyPhotoinactivationPhotosystemII2017] who found a lower cost of growth, due to decreased photoinactivation of PSII under red, compared to blue, wavebands (Figure \@ref(fig:BluevsRedPurFitsPlots)G,H).  Interestingly, this protective effect of red light disappears for MIT9313 growing under 2.5 µM O~2~, possibly because photoinactivation is strongly suppressed under this low [O~2~] (Figure \@ref(fig:BluevsRedPurFitsPlots)I). For distinct fits for different photoperiod fits refer to Figure \@ref(fig:PhotoperiodPurFitsPlots) G,H and I.
